Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-02 paper/paper.tex
message

\paragraph{Learning} Learning took place by stepwisely adapting the weights
$\omega\Ix{read}$ so that the dynamics $t\mapsto r_i(t)$ of the readout
rates should eventually match a given periodic input pattern $t\mapsto
a_i(t)$ as accurately as possible. To update $\omega\Ix{read}$ we chose
a variant of the FORCE algorithm \citep{FORCE} that rapidly modifies the
feedback loop to keep the errors $|r_i(t) - a_i(t)|$ small from the
beginning on.

>>>>

\paragraph{Challenges}

\paragraph{Learning} Learning took place by stepwisely adapting the weights
$\omega\Ix{read}$ so that the dynamics $t\mapsto r_i(t)$ of the readout
rates should eventually match a given periodic input pattern $t\mapsto
r'_i(t)$ as accurately as possible. To update $\omega\Ix{read}$ we chose
a variant of the FORCE algorithm \citep{FORCE} that rapidly modifies the
feedback loop to keep the errors $|r_i(t) - r'_i(t)|$ small from the
beginning on.
